Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-09-13 RNARedPrint.tex
Fix PS(Y)

Since our algorithms iterate over specific sets of sequence positions, we moreover define
the \Def{set of partial sequences $\partseqs(\Y)$ determining $\Y\subseteq\{1,\dots,n\}$} as
$$
\partseqs(\Y)=\{ x\mapsto v \mid \text{$x\in\Y$ and $v\in \{\Ab,\Cb,\Gb,\Ub\}$}\}.
$$
%
We assume several properties of the given cluster tree (reflecting $\F$), which otherwise could be easily obtained:
\begin{itemize}
\item
$T$ is
connected and contains a dedicated node $r$, with
$\chi(r)=\varnothing$ and $\phi(r)=\varnothing$. If such a root does not exist, it can be added to the tree decomposition and connected to one node in each connected component of $T$.
\item
all edges in the tree decompostion are oriented towards this root.
\item
all sets $\difference{u}{v}$ are singleton: for any given
cluster tree, an equivalent (in term of treewidth) cluster tree can
always be obtained by inserting at most $\Theta(|\X|)$ additional
clusters.
\end{itemize}

>>>>

Since our algorithms iterate over specific sets of sequence positions, we moreover define
the \Def{set $\partseqs(\Y)$ of all partial sequences determining the positions of $\Y\subseteq\{1,\dots,n\}$} in all combinations of nucleotides $\{\Ab,\Cb,\Gb,\Ub\}$.
%
We assume several properties of the given cluster tree (reflecting $\F$), which otherwise could be easily obtained:
\begin{itemize}
\item
$T$ is
connected and contains a dedicated node $r$, with
$\chi(r)=\varnothing$ and $\phi(r)=\varnothing$. If such a root does not exist, it can be added to the tree decomposition and connected to one node in each connected component of $T$.
\item
all edges in the tree decompostion are oriented towards this root.
\item
all sets $\difference{u}{v}$ are singleton: for any given
cluster tree, an equivalent (in term of treewidth) cluster tree can
always be obtained by inserting at most $\Theta(|\X|)$ additional
clusters.
\end{itemize}
